---
title: "Data Import"
output: github_document
---

Option command i opens the code chunk

```{r setup}
library(tidyverse)
```

## Read in some data

Read in the litters dataset.
Janitor cleans up the names - converts to lowercase, replaces spaces and puncts w _, removes special characters, makes names syntactically 

```{r}
litters_df = read_csv("./data/FAS_litters.csv")
litters_df = janitor::clean_names(litters_df)
```



## Take a look at the data
Printing in the console
```{r}
litters_df
```

Gives the first 6 rows
```{r}
head(litters_df)
```

Last few rows
```{r}
tail(litters_df)
```

Skim is the only function in the skimr package, not downloading all of skimr
```{r}
skimr::skim(litters_df)
```

Put View(litters_df) shows the full dataset, but don't put this in RMD only in the console!

Character variable- mix of letters and numbers
double- particular kind of number, missing variables coded as NA

Can type in ?read_csv to look at the help function 

## Options to read_csv

```{r}
litters_df = read_csv("./data/FAS_litters.csv", skip = 10, col_names = FALSE)
```


```{r all of these are missing na = c}
litters_df = read_csv("./data/FAS_litters.csv", na = c("", "NA", ".", 999)
```

```{r}
litters_df = read_csv("./data/FAS_litters.csv"
```

checkout `read_csv()` for more information

